Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-07 proposalPres.tex
Update proposalPres.tex
I added to the literature review and System Architecture slides, and changed some things in the System Identification slide.

\begin{frame}{Literature Review}
  \begin{block}{Existing Solution}
 \begin{itemize}
        \item Use of System Identification Toolbox in Matlab to create models from data~\cite{Adnan2010}
	 \begin{itemize}
		    \tiny
		    		\item Offers a variety of model choices
				\item Needs a large amount of raw data to produce an accurate model
	\end{itemize}
	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
	 \begin{itemize}
		    \tiny
		    		\item Allows the use of traditional analysis methods to create a model 
				\item More room for error during calculations
	\end{itemize}
	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
	 \begin{itemize}
		    \tiny
		    		\item Can model systems with small non-linearities 
				\item Mechanical components replaced by electrical components 
	\end{itemize}
\end{itemize}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{System Identification}
  \begin{block}{System Identification}
 \begin{itemize}
        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system. The goal of the system identification methodology is to get an accurate estimation of the system response to any given input. Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}
  \begin{block}{}
 \begin{itemize}
        \item 
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}{Literature Review}
  \begin{block}{Existing Solutions}
 \begin{itemize}
        \item Use of System Identification Toolbox in Matlab to create models from data~\cite{Adnan2010}
	 \begin{itemize}
		    \tiny
		    		\item Offers a variety of model choices
				\item Needs a large amount of raw data to produce an accurate model
	\end{itemize}
	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
	 \begin{itemize}
		    \tiny
		    		\item Allows the use of traditional analysis methods to create a model 
				\item More room for error during calculations
	\end{itemize}
	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
	 \begin{itemize}
		    \tiny
		    		\item Can model systems with small non-linearities 
				\item Mechanical components replaced by electrical components 
	\end{itemize}
	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
	\begin{itemize}
	\tiny
		\item Fourth order ARX model ended up giving the best fit
	\end{itemize}
\end{itemize}
  \end{block}
    % \begin{figure}[b]
    %     \centering
    %     \includegraphics[width=0.45\textwidth]{figs/img/CompaRob}
    %     \caption{CompaRob}
    %     %\label{fig:sysBlockDiag}
    % \end{figure}
\end{frame}

@@

\begin{frame}{System Identification}
  \begin{block}{System Identification}
 \begin{itemize}
        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system. The goal of the system identification methodology is to get an accurate estimation of the system response to any given input. Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
\end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}
  \begin{block}{System Architecture}
 \begin{itemize}
        \item The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems
\end{itemize}
  \end{block}
\end{frame}
